Pythran: Turning Python Modules into Optimized C++ Meta-Programs

### 2013-10-02 doc/papers/cc2014/tool.tex

To achieve these goal, the presentation relies on \begin{inparaenum} \item User
    stories that illustrates the basic \ac{CLI} of the Pythran compiler,
(\S\ref{sec:cli}).  \item Code snippets related to analyse and passes
    implemented in Pythran (\S\ref{sec:code-analyse},
\S\ref{sec:code-transformation}). \item A sample implementation of parallel map
detection in the Pythran compiler infrastructure (\S\ref{sec:pmap}).  \item
Benchmarks from the \emph{Python Benchmark} codebase that compare several
Python compiler in the context of numerical applications
(\S\ref{sec:python-benchmarks}). \end{inparaenum}

>>>>

To achieve these goals, the presentation relies on \begin{inparaenum} \item User
    stories that illustrates the basic \ac{CLI} of the Pythran compiler,
(\S\ref{sec:cli}).  \item Code snippets related to analyse and passes
    implemented in Pythran (\S\ref{sec:code-analyse},
\S\ref{sec:code-transformation}). \item A sample implementation of parallel map
detection in the Pythran compiler infrastructure (\S\ref{sec:pmap}).  \item
Benchmarks from the \emph{Python Benchmark} codebase that compare several
Python compiler in the context of numerical applications
(\S\ref{sec:python-benchmarks}). \end{inparaenum}
